Placeholder

### 2021-02-05 Paper_Histograms.Rmd
Collapsed the personality disorder clusters to one variable for the diagnosis retro plot

@@

dat.retro_diagnosis_variables <- data.frame(c("depressive disorders", "anxiety disorders", "eating disorders", "obsessive compulsive disorders", "psychotic disorders", "autism spectrum disorder", "attention deficit hyperactivity disorder", "personality cluster a", "personality cluster b", "personality cluster c", "mania hypomania bipolar or manicdepression", "posttraumatic stress disorder ptsd", "control"))

@@

>>>>

```{r Collapse personality disorder clusters}

dat.retro <- dat.retro %>% 
  mutate(personality_disorder_numeric =
           case_when(
             personality_cluster_a_numeric == 1 | personality_cluster_b_numeric == 1 | personality_cluster_c_numeric == 1 ~ 1,
             personality_cluster_a_numeric == 0 & personality_cluster_b_numeric == 0 & personality_cluster_c_numeric == 0 ~ 0
           ))

#Check that it worked
head(dat.retro$personality_cluster_a_numeric, 10)
head(dat.retro$personality_cluster_b_numeric, 10)
head(dat.retro$personality_cluster_c_numeric, 10)
head(dat.retro$personality_disorder_numeric, 10)

@@

dat.retro_diagnosis_variables <- data.frame(c("depressive disorders", "anxiety disorders", "eating disorders", "OCDs", "psychotic disorders", "aSD", "ADHD", "personality cluster a", "personality cluster b", "personality cluster c", "mania hypomania bipolar or manicdepression", "PTSD", "control"))

@@

```{r GLAD/EDGI NBR and RAMP diagnosis retro}

dat.retro_diagnosis_type %>% 
  mutate(diagnosis_plot = fct_reorder(diagnosis, -count)) %>% 
  ggplot(aes(x = diagnosis_plot, y = count)) +
  geom_bar(stat = "identity") +
  scale_x_discrete(guide = guide_axis(n.dodge = 3)) +
  theme_minimal() +
  labs(x = "",
       y = "")
